A multi-dimensional extension of the Lightweight Temporary Compression method

### 2018-10-05 paper.tex
mass note

@@

In practice, It's needed to transmit raw data which has multi-parameters to clients e.g. Accelerometer, Euler Angle and Magnetometer etc. LTC not work well when we transmit multi-parameters data, cause if we just implement LTC for each parameter, the difference between estimation and origin could exceed error margin which was set in advance. For instance, there is a data $(x, y)$ with two parameters, and using LTC for both parameter respectively. According to LTC method $\mid{\hat{x}-x}\mid\leqslant \epsilon$~\cite{jalaleddine1990ecg}, the estimation may be $(\hat{x}=x+\epsilon, \hat{y}=y+\epsilon)$, then the difference between estimation and original data $(x,y)$ is which is bigger than error margin predefined. In this case, we design a new algorithm, which is multi-parameter version of LTC, and it also work with any type of distance. In standard LTC method, it checks if there is overlapping part between new sector area and recorded range. However, in our multidimensional method, we will map every data point into same time-stamp e.g. $t_0$. It is convenient for us to calculate distance between them and check if overlapping range exists. we provide Multidimensional-LTC with Euclidean and Manhattan distance in below.
\subsection{Multidimensional LTC with Manhattan distance}
In practice, Multidimensional LTC is same as implementing LTC in each parameter respectively. But we did some changes in our method. Assume $(x_{i1}, x_{i2}, ..., x_{in},t_i)$ is the $i_{th}$ coming data with n-dimension, and a base data point Z  $(z_{1}, z_{2}, ..., z_{n},t_z)$~\cite{schoellhammer2004lightweight}. We map each coming data to $t_1$ time-stamp and create a bounding box for recording overlapping range which includes upper and lower bound for each dimension base on $t_1$. cause the time different between two adjacent data, so the $i_th$ data after mapping is $(\{\hat{x_{ij}}=z_j + \frac{x_{ij}-z_{j}}{t_i-t_z} \mid1\leqslant{j}\leqslant{n}\},t_i)$. After that updating tolerance range by adding designed error margin which after mapping $\frac{\epsilon}{t_i-t_z}$ on $\hat{x_{ij}}, j={1...n}$ with Manhattan distance. checking if there is overlap between tolerance and bounding box.The algorithm is as follows.

\note{not clear about Manhattan distance, in my opinion for each axis the distance less than $EPSILEN/t_i-t_0$ + bounding box length}

@@

\subsection{Multidimensional LTC with Euclidean distance} 
In Euclidean distance version, we also map the coming data into same time-stamp. The difference with Manhattan distance version is that recording overlapping part with a post-designed model is difficult, which need retain several arcs in 2-dimension, or convex surfaces in 3-dimension. In our method, we will record all tolerance range for every mapped data which come from base data point until coming data point, in order to checking if there is intersection among them. In the rest of this section, we describe examples for 2-dimensional and 3-dimensional version. After that, we extend the method for n-dimension.
\begin{itemize}
\item \textbf{2-dimensional LTC in Euclidean distance:}In this situation, the tolerance range after mapping is a disk. After initializing base data point \textit{z}, for each coming data point need to be mapped into a same time-stamp, and heck if there is a intersection amount disks in disks set and new mapped coming data. Therefore, a algorithm is need to determine whether \textit{n} disks intersect or not.
\item \textbf{3-dimensional LTC in Euclidean distance:}In 3-dimension, cause of the preassigned error margin, the disks become balls with one extra axis. So In 3-dimension whether \textit{n} balls intersect need to be check.
\end{itemize}

@@

\subsection{Experiment 1: energy reduction on the Neblina}
\begin{itemize}
    \item Data set: 
    \item Experiment Condition: 
    \item Result: 
    \item Conclusion: 
\end{itemize}

>>>>

LTC会记录一个范围，from which 可以找到一条直线，代替original data，并且保证 保证度，或者 distort。 当一个新data来的时候，base data会与 data+/-EPSILON 创建一个 临时的范围， 如果这个范围与 已经记录的范围 存在 交集，那么更新已记录的范围， 如果交集为空，则transmit base data，并将，已经记录的范围的median，and current timesamp - 1 作为 base point的值和timestamp. 以此循环。
画个图。
只需要 constant Memory。

@@

In practice, It's needed to transmit raw data which has multi-parameters to clients e.g. Accelerometer, Euler Angle and Magnetometer etc. LTC not work well when we transmit multi-parameters data, cause if we just implement LTC for each parameter, the difference between estimation and origin could exceed error margin which was set in advance. For instance, there is a data $(x, y)$ with two parameters, and using LTC for both parameter respectively. According to LTC method $\mid{\hat{x}-x}\mid\leqslant \epsilon$~\cite{jalaleddine1990ecg}, the estimation may be $(\hat{x}=x+\epsilon, \hat{y}=y+\epsilon)$, then the difference between estimation and original data $(x,y)$ is which is bigger than error margin predefined. In this case, we design a new algorithm, which is multi-parameter version of LTC, and it also work with any type of distance. In standard LTC method, it checks if there is overlapping part between new sector area and recorded range. However, in our multidimensional method, we will map every data point into same time-stamp e.g. $t_0$. It is convenient for us to calculate distance between them and check if overlapping range exists. we provide Multidimensional-LTC with Euclidean and Manhattan distance in below.

\section{Implementation}
Our code is available at ... (make a clean release!)

\subsection{Multidimensional LTC with Manhattan distance}
In practice, Multidimensional LTC is same as implementing LTC in each parameter respectively. But we did some changes in our method. Assume $(x_{i1}, x_{i2}, ..., x_{in},t_i)$ is the $i_{th}$ coming data with n-dimension, and a base data point Z  $(z_{1}, z_{2}, ..., z_{n},t_z)$~\cite{schoellhammer2004lightweight}. We map each coming data to $t_1$ time-stamp and create a bounding box for recording overlapping range which includes upper and lower bound for each dimension base on $t_1$. cause the time different between two adjacent data, so the $i_th$ data after mapping is $(\{\hat{x_{ij}}=z_j + \frac{x_{ij}-z_{j}}{t_i-t_z} \mid1\leqslant{j}\leqslant{n}\},t_i)$. After that updating tolerance range by adding designed error margin which after mapping $\frac{\epsilon}{t_i-t_z}$ on $\hat{x_{ij}}, j={1...n}$ with Manhattan distance. checking if there is overlap between tolerance and bounding box.The algorithm is as follows.

\note{not clear about Manhattan distance, in my opinion for each axis the distance less than $EPSILON/t_i-t_0$ + bounding box length}

@@

\subsection{Multidimensional LTC with Euclidean distance}
In Euclidean distance version, we also map the coming data into same time-stamp. The difference with Manhattan distance version is that recording overlapping part with a post-designed model is difficult, which need retain several arcs in 2-dimension, or convex surfaces in 3-dimension.
In our method, we will record all tolerance range for every mapped data which come from base data point until coming data point, in order to checking if there is intersection among them.
画图；
写一个3-D的例子，并解释一下 算法
assume 有一个 3D 的数据 (x,y,z, t_n)， 会被mapping到 (....) with error sphere EPSILON/(t_n - t_1).and check if there is public intersection with list of circle which recorded.
首先确定x的范围，C_maxX = Min=1.n(c_i.x + E/i), C_minX = Max=1.n(c_i.x - E/i), if C_maxX < C_minX, means there is no public intersection amount those circles.
after that 使用二分法 mid_x=(C_maxX + C_minX)/2, with x=mid_x computer bounding range of y-axis, 并对y轴继续使用 二分法，在z-axis 上计算 C_minZ and C_maxZ, 如果 C_maxZ > C_minZ 说明 在x=mid_x, y=mid_y 这条线上 存在一个或多个点 在intersection amount those circles. so 我们可以确认 确认交集的存在，并且 把点(mid_x, mid_y, mid_z) 保存下来，以便将来更新base point.

通过这个 例子 我们可以把 3-D 延伸到 n-D。

In the rest of this section, we describe examples for 2-dimensional and 3-dimensional version. After that, we extend the method for n-dimension.
\begin{itemize}
\item \textbf{2-dimensional LTC in Euclidean distance:}In this situation, the tolerance range after mapping is a disk. After initializing base data point \textit{z}, for each coming data point need to be mapped into a same time-stamp, and heck if there is a intersection amount disks in disks set and new mapped coming data. Therefore, a algorithm is need to determine whether \textit{n} disks intersect or not.
\item \textbf{3-dimensional LTC in Euclidean distance:}In 3-dimension, cause of the preassigned error margin, the disks become balls with one extra axis. So In 3-dimension whether \textit{n} balls intersect need to be check.
\end{itemize}

@@

\subsection{Experiment 1: energy reduction on the Neblina}

The capacity of battery in Neblina is 100mAh, and the battery usage would not change too much, because it contans others fusion method which will running when turning on the Neblina.
In 50Hz sensor sampling rate, the average usage electric current for transmit accelerometers data is 2.0mA. It means Neblina could tranmit accelerometers data constantly in 100/2.0=50 hours.
After compressed by LTC-Manhattan method, the average usage electric current is 1.95mA. It just extend Neblina lift abou 1.28 hours.
But in 200Hz sampling rate. The electric before and after compression are 3.5 and 2.9 respectively. The running time of Neblina would be extended about 5.9 hours/

\begin{itemize}
    \item Data set: human activities, running, walking, jogging and work behind desk.
    \item Experiment Condition: work with neblina.
    \item Result:
    \item Conclusion:
\end{itemize}
